Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2015-08-23 doc/GMP2015/revision_3/appendix_proofs.tex
Updated paper to say algo is O(V^4). However, I also provide a sketch of what I believe to be a working O(V^3). Updated todo's.
Lots of work on Revision 3, getting close.

\begin{observation}\label{observation:no_edges_between_diff}
Take $R_i=C\setminus C_i$ and $R_j=C\setminus C_j$. If $C_i\cup C_j$ is isostatic, then there can be no edges in $C$ between the vertices of $R_i$ and $R_j$.
\end{observation}

@@

\begin{proof} (Of Lemma \ref{lemma:combined_lemma}, Point \ref{lemma:wc_intersection_makes_all_wc})

The alternative phrasing is as in Lemma \ref{lemma:combined_lemma}, Point \ref{lemma:wc_intersection_is_C}.

Take $R_i=C\setminus C_i$, $R_j=C\setminus C_j$, and $D_{i,j}=C_i\cap C_j=(C\setminus R_i)\setminus R_j$ (note that $R_j\subset C_i$, $R_i\subset C_j$ and $D_{i,j}\subset C_i,C_j$). Furthermore, take the proper subgraphs $R'_i\subset R_i$, $R'_j\subset R_j$, and $D'_{i,j}\subset D_{i,j}$ that are non-empty.

Assume that there is a third isostatic vertex-maximal proper subgraph $C_k$ (with $C'_k=C\setminus C_k$). There are $3\times 3\times 3 = 27$ possible cases for what this subgraph could be.

Without loss of generality, all graphs are the induced subgraphs of $C$.

@@

Since $D_{i,j}\subset C_i, C_j$ it means that $C_k\cup C_i = C_k \cup C_j = C$, thus proving the Lemma.
%
% \todo{Need a figure?}
\end{proof}

@@

We adopt the following algorithm. Choose the 2 bodies to pin to by choosing a node $b$ in $T$ and looking at its children. From Observation \ref{rem:1dofcanon}, we know that the children can only share  a single pin or a sub-graph. Pin the new body to bodies in two separate children. Doing so will ensure that all children of $b$ will have 1-dof and all ancestors of $b$ (including $b$) will now be isostatic.

>>>>

\begin{proof}
    % (Of Lemma \ref{lemma:combined_lemma}, Point \ref{lemma:wc_intersection_makes_all_wc})
    %
    Take two children of node $C$, called $C_i$ and $C_j$. Let $R_i$ be the graph induced in node $C$ by the edge set of $C$ minus the edge set of child $C_i$ ($C\setminus C_i$ for convenience); let $R_j=C\setminus C_j$. Let $D_{i,j}=C_i\cap C_j=C\setminus (R_i\cup R_j)$. Let $R'_i\subset R_i$, $R'_j\subset R_j$, and $D'_{i,j}\subset D_{i,j}$, and take these proper subgraphs to be non-empty.

    If there are two children ($N=2$) then the proof is simple, it follows from the definition of a DR-plan: the union of the children is the parent which is isostatic. Assume that $N>2$ and take a third child, called $C_k$.
    % Let $R_k=C\setminus C_k$.
    We want to determine what $C_k$ can be, in terms of $i$ and $j$. $C_k$ can possibly be composed of an element from $\{\emptyset, D'_{i,j}, D_{i,j}\}$, an element from $\{\emptyset, R'_i, R_i\}$, and an element from $\{\emptyset, R'_j, R_j\}$, for a total of 27 cases. We will exhaustively show that it must be $R_i\cup R_j\cup D'_{i,j}$. First, we make the following observation:

    \begin{observation}\label{observation:no_edges_between_diff}
        If $C_i\cup C_j$ is isostatic, then there can be no edges in $C$ between the vertices of $R_i$ and $R_j$.
    \end{observation}

@@

    % Take $R_i=C\setminus C_i$, $R_j=C\setminus C_j$, and $D_{i,j}=C_i\cap C_j=(C\setminus R_i)\setminus R_j$ (note that $R_j\subset C_i$, $R_i\subset C_j$ and $D_{i,j}\subset C_i,C_j$). Furthermore, take the proper subgraphs $R'_i\subset R_i$, $R'_j\subset R_j$, and $D'_{i,j}\subset D_{i,j}$ that are non-empty.

    % Assume that there is a third isostatic vertex-maximal proper subgraph $C_k$ (with $C'_k=C\setminus C_k$). There are $3\times 3\times 3 = 27$ possible cases for what this subgraph could be.

    % Without loss of generality, all graphs are the induced subgraphs of $C$.

@@

    Since $D_{i,j}\subset C_i, C_j$ it means that $C_k\cup C_i = C_k \cup C_j = C$, thus proving Point \ref{lemma:wc_intersection_makes_all_wc}.
    The alternative phrasing of this Point is straightforward from Point \ref{lemma:wc_intersection_is_C}.
    %
    % \todo{Need a figure?}
\end{proof}

@@

We adopt the following algorithm. Choose the 2 bodies to pin to by choosing a node $b$ in $T$ and looking at its children. From Observation \ref{rem:1dofcanon}, we know that the children can only share  a single pin or a subgraph. Pin the new body to bodies in two separate children. Doing so will ensure that all children of $b$ will have 1-dof and all ancestors of $b$ (including $b$) will now be isostatic.
